\chapter{Glossary}
\label{chap:glossary}

Here, we compile a list of terms and definitions relevant to the study of supernovae.
\\
\defineterm{Supernova}{a star that suddenly increases greatly in brightness because of a catastrophic explosion that ejects most of its mass.}
\defineterm{Hydrostatic equilibrium}{A condition that requires the accelerations due to the forces interior to the star to be neglibible. It is enforced by requiring that a pressure gradient $dP/dr$ must exist to counteract the force due to gravity. See \autoref{sec:hydro-eq}.}
\defineterm{Mass conservation law}{A condition which states how the interior mass of a star must change with distance from the center. See \autoref{sec:hydro-eq}.}
\defineterm{Pressure integral}{An expression that allows the pressure of an ideal gas to be computed given a distribution function of momenta. See \autoref{sec:pressure-equation-of-state}.}
\defineterm{Mean molecular weight}{The average mass of a particulate gas, scaled by the mass of a hydrogen atom. Typically represented with $\mu$. See \autoref{sec:pressure-equation-of-state}.}
\defineterm{Fermi-Dirac distribution}{An alternative to the Maxwell-Boltzmann distribution which considers the Heisenberg uncertainty principle as well as the Pauli exclusion principle. This distribution is extremely important, especially for compact source such as white dwarfs and neutron stars.}
\defineterm{Virial theorem}{A theorem which states that the total energy of a system of particles at equilibrium is one-half of the system's potential energy.}
\defineterm{Single-degenerate (SD) channel}{A non-degenerate star accretes onto a white dwarf companion, and the white dwarf explodes as it approaches the Chandrasekhar limiting mass}
\defineterm{Double-degenerate (DD) scenario}{Two white dwarfs in a binary system lose angular momentum and potential energy due to gravitational wave radiation and they merge. The remnant's instability powers the explosion. }
\defineterm{Core-degenerate (CD) scenario}{A white dwarf merges with an asymptotic giant branch (AGB) star and explodes. }
\defineterm{White dwarf-white dwarf}{Two white dwarfs collide and explode. This scenario can only plausibly explain at most a few percent of all SNe Ia.}
\defineterm{Nebular phase}{A phase of a supernova where the resulting nebula becomes optically thin and primarily illuminated by the radioactive decay of isotopes. During this phase, the observed spectrum changes from having blackbody characteristics with atmospheric absorption lines imposed to an emission line spectrum rich in spectral fingerprints from the newly synthesized elements.}